Data Processing: Mission Assignments

### 2021-12-10 code/processing_code/processing-missions.Rmd
Documentation Updates
Missions Processing Update

* Raw data summarization and overview
* Removal of irrelevant variables
* Summarization of mission costs for each state and disaster declaration
* Feature engineering to create cost share proportions
* Saving the processed dataset as an .rds

@@

## Load Raw Data
Load the raw data downloaded from provided hyerlink.
```{r load data}
#path to data
#note the use of the here() package and not absolute paths
data_location_ma <- here::here("data", "raw_data", "MissionAssignments.csv")

>>>>

* Raw data summarization and overview
* Removal of irrelevant variables
* Summarization of mission costs for each state and disaster declaration
* Feature engineering to create cost share proportions and number of government agencies involved in the response
* Cleaning the state variable names to match the other data sources
* Saving the processed dataset as an .rds

@@

## Load Raw Data
Load the raw data downloaded from provided hyperlink.
```{r load data}
#path to data
#note the use of the here() package and not absolute paths
data_location_ma <- here::here("data", "raw_data", "MissionAssignments.csv")
